Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 discussion.tex

In existing R tools, the command prompt is used to try things out. It is very
fast and there is no commitment: nothing gets saved and there is nothing to
later clean up. In contrast, in RCloud's notebook interface, the extra cells need
to get deleted later, and there seems to be a mental burden that \textit{bad stuff
is getting saved}.

@@

The system also needs to help users curate their notebooks. If a notebook
has been superceded by one of its forks, a user who opens it should be
warned. If a notebook has been deleted, but someone still has a link to it,
it should be clear that the notebook is dead. And operations on multiple
notebooks and folders of notebooks should be supported to make curation
easier.

>>>>

In existing R tools, the command prompt is used to try things out. It is very
fast and there is no commitment: nothing gets saved and there is nothing to
later clean up. In contrast, in RCloud's notebook interface, the extra cells need
to get deleted later, and there seems to be a mental burden that \emph{bad stuff
is getting saved}.

@@

The system also needs to help users curate their notebooks. If a notebook
has been deleted or superceded by one of its forks, a user who opens it
should be warned. And operations on multiple notebooks and folders of
notebooks should be supported to make curation easier.
